\documentclass{article}
\usepackage[utf8]{inputenc}
%\usepackage{booktabs}
\usepackage{physics}
\usepackage{url}
\usepackage{braket}
\usepackage{natbib}
%\usepackage{mandi}
\usepackage{verbatim} % for comment environment : bug finding
\begin{document}
\title{Master Project}
\author{Tejas Shetty}
%\address{221B, Baker Street, London, UK}
\date{\today} % or can be any other day
\maketitle
One convenient way to set this up if you're planning to use the same files across multiple projects is to organize things as follows:

Create a “master” project containing your common files e.g. .bib, .cls, .sty, graphics, etc.
In your “child” projects, click the “Add file” button at the top of the project side bar.
Select “File from other project”, and navigate to your “master” project, and select the file that you need.
You will now be able to used the linked file in your “child” project.

If you’ve modified the original copy of the files in the “master” project, remember to right-click on the linked .bib in the “child” projects and then “Refresh” (or click on the file and click on the Refresh button in the file preview that appears), to pull in the changes.
\cite{maday2003new}
%\url
{https://www.overleaf.com/help/226-can-i-share-files\\
-e-dot-g-bib-and-some-graphics-across-my-projects.W5qHGd0zbCI}\\
%(Type your content here.)

\section{How to use/ maintain}
\subsection{Use}
Whenever you need to include a reference in your article, go to mylit.bib. Press command + F or Ctrl + F to find the article corresponding to your search string. If found copy the bib label. In your project refresh mylit.bib and use it in the cite command.    
\par
If this fails see the reference list in the PDF of this project and see if you hit upon anything. (You may download it and do the same press command + F or Ctrl + F thing). Then see the reference no and note it down.  Add 200 to this no and call it cite no. Go to the line corresponding to the cite no on the source of this file. Copy the biblabel from the argument of the nocite command on this file. 
\subsection{Maintenance}
Before adding search it in mylit.bib, etc as above to see if it already exists.
To add a bibliographic entry to this project search it on  web (e.g google, etc ) and copy bibtex information  from  google scholar, semantic scholar, etc and paste it in mylit.bib. Secondly, one must add
add the biblabel to the table. 
\par
The most important thing is to add it to the nocite collection at the end. Also fix errors as soon as they apppear.

\section{Biblabels}
\begin{table}[ht]
\centering
\begin{tabular}{l|l}
Known Name & Bib label \\\hline
petta & petta \\
Zhu and Rabitz & zhu1998rapid\\
Manday and Tutinici & maday2003new\\
Grape Khaneja & khaneja2005optimal\\
GOAT & machnes2015gradient\\
CRAB & doria,caneva2011chopped\\
DCRAB & rachnes2015dressing\\
hotgates & hot gates\\
tannor(krotov) & tannor1992control\\
lindblad & lindblad1976g\\
suri thermal & 2018EPJST.227..203S
\end{tabular}
\caption{\label{tab:Important  Biblabel}Important  Biblabel}
\end{table}






































\newpage 
%% citations available
\nocite{petta}
\nocite{lindblad1976g}
\nocite{hot-gates}
\nocite{2018EPJST.227..203S}
\nocite{maday2003new}
\nocite{tannor1992control}
\nocite{zhu1998rapid}
\nocite{khaneja2005optimal}
\nocite{caneva2011chopped}
\nocite{doria}
\nocite{machnes2015gradient}
\nocite{2012JChPh.136j4103R}
\nocite{Whatisqubit}
\nocite{nielsen2004quantum}
\nocite{wiki:resonator}
\nocite{Tejas_APS1}
\nocite{gerry2005introductory}
\nocite{traxler2009decoherence}
\nocite{bertlmann2008theoretical}
\nocite{sakurai1995modern}
\nocite{churchill1990complex}
\nocite{breuer2002}
\nocite{percival1998}
\nocite{PaolaMIT2012}
\nocite{2006quant.ph.12095L}
\nocite{jcreviewshoreknight}
\nocite{larson2007dynamics}
\nocite{cambridgestate}
\nocite{jaynes1963comparison}
\nocite{cummings1962comparison}
\nocite{wichterich2007modeling}
\nocite{aravind1984two}
\nocite{haroche1985radiative}
\nocite{yoo1985dynamical}
\nocite{barnett1985thermofield}
\nocite{barnett1986dissipation}
\nocite{meystre2013elements}
\nocite{kien1991interaction}
\nocite{hinds1991advances}
\nocite{meystre1992v}
\nocite{filipovicz1985rydberg}
\nocite{knight1986quantum}
\nocite{meschede1985one}
\nocite{rempe1986one}
\nocite{brune1987realization}
\nocite{horoche1989cavity}
\nocite{gorini1976completely}
\nocite{brasil2011}
\nocite{brasil2011protecting}
\nocite{nielsen2003computaccao}
\nocite{caldeira1983caldeira}
\nocite{davies1976quantum}
\nocite{alicki2007general}
\nocite{adler2000derivation}
\nocite{adler2000corrigendum}
\nocite{peres2000classical}
\nocite{mechnics1977claude}
\nocite{schleich2001quantum}
\nocite{rach2015dressing}
\nocite{d2007introduction}
\nocite{Batzri1973}
\nocite{Sackmann1995a}
\nocite{Boal2012}
\nocite{Smith99} %Douglas E Smith
%\nocite{Smith99HOM} %not found
\nocite{SunHI03}
\nocite{luding94}
\nocite{rich-mart92}
\nocite{einstein}
\nocite{latexcompanion}
\nocite{knuthwebsite}
\nocite{qutip2}
\nocite{qutip1}
\nocite{2019arXiv190205779H}
\nocite{}
\nocite{}
\nocite{}
\nocite{}
\nocite{}
\nocite{}
\nocite{}



\begin{table}[ht]\label{tab:less Important  Biblabel}
\centering
\begin{tabular}{l|l}
Known Name & Bib label \\\hline
hotgates & hot-gates\\
gerry & gerry2005introductory\\
traxler & traxler2009decoherence\\
bertlmann & bertlmann2008theoretical\\
sakurai & sakurai1995modern\\
churchill & churchill1990complex\\
breuer & breuer2002\\
Paola & PaolaMIT2012\\
2006quant.ph  & 2006quant.ph.12095L\\
Jcreviewshore &  jcreviewshoreknight\\
larson  & larson2007dynamics\\
cambridgestate  & cambridgestate\\
jaynes1963 & jaynes1963comparison\\
cummings1962 & cummings1962comparison\\
wichterich  & wichterich2007modeling\\
Aravind & aravind1984two\\
haroche  & haroche1985radiative\\
yoo  & yoo1985dynamical\\
barnett1985 & barnett1985thermofield\\
barnett1986 & barnett1986dissipation\\
meystre2013 & meystre2013elements\\
kien  & kien1991interaction\\
hinds  & hinds1991advances\\
meystre  & meystre1992v\\
filipovicz  & filipovicz1985rydberg\\
knight  & knight1986quantum\\
meschede  & meschede1985one\\
rempe1986 & rempe1986one\\
brune  & brune1987realization\\
horoche  & horoche1989cavity\\
gorini  & gorini1976completely\\
brasil  & brasil2011\\
brasilp & brasil2011protecting\\
nielsen2003 & nielsen2003computaccao
\end{tabular}
\caption{less Important  Biblabel 1}
\end{table} 
\newpage


\newpage
\begin{table}[ht]
    \centering
    \begin{tabular}{c|c}
     Known Name & Bib label \\\hline
     caldeira1983 & caldeira1983caldeira\\
     davies  & davies1976quantum\\
     alicki  & alicki2007general\\
     adler  & adler2000derivation\\
     adlerc & adler2000corrigendum\\
     peres2000 & peres2000classical\\
    mechnics  & mechnics1977claude\\
    schleich  & schleich2001quantum\\
    rach2015 & rach2015dressing\\
    d2007 & d2007introduction\\
    Batzri  & Batzri1973\\
    Sackmann  & Sackmann1995a\\
    Boal  & Boal2012\\
    SunH & SunHI03\\
    Ludin & luding94\\
    rich  & rich-mart92\\
    Einstein & einstein\\
    Latexcompanio & latexcompanion\\
    Knuthwebsite & knuthwebsite\\
    qutip2 & qutip2\\
    qutip1 & qutip1 \\
    2019arXiv190205779H & 2019arXiv190205779H
    \end{tabular}
    \caption{less important biblabel 2}
    \label{tab:less important biblabel 2}
\end{table}
\newpage



%%%%%%%%
\bibliographystyle{unsrt} %stylename
\bibliography{mylit} %.bib file name

%%%%%%%%
%\begin{thebibliography}{}
%\bibitem{}
%Sets the bibliography style to iitbauthyr and imports the 
%bibliography file "mylit.bib".
%\bibliographystyle{iitbauthyr} %stylename
%\bibliography{mylit} %.bib file name 
%\end{thebibliography}
%\end{bib}
\end{document}
